R for Clinical Study Reports and Submission

### 2021-10-27 slides/workshop-slides.Rmd
update slides

```{r, eval = FALSE, include = FALSE}
rmarkdown::render("slides/workshop-slides.Rmd")
```

@@

@@

- Training Material: https://r4csr.org/
- Demo project: https://github.com/elong0527/esubdemo
- R Consortium FDA submission pilot: https://github.com/RConsortium/submissions-pilot1

>>>>

```{r, eval = FALSE, include = FALSE}
rmarkdown::render("workshop-slides.Rmd")
```

@@

## Training Objective

- Learning how to create tables for clinical study reports.
- Learning how to organize a clinical development project.
- Learning how to prepare eCTD submission package to FDA.

> The tool, process and format may be different in different organization/company.
> We only provide a recommended way to address them.

## Acknowledgement

- Team members from Merck & Co. 
  + [We are hiring!](https://jobs.merck.com/bards) 
  + Contact us if interested.

- [Contributors](https://r4csr.org/) of the training materials.
  + Please consider to submit issues or PR in the repo.

- [R consortium](https://www.r-consortium.org/projects/isc-working-groups)
  + R validation hub
  + Submission working group
  + R Tables for Regulatory Submission (RTRS) working group
  + Please consider to join and contribute to a working group.

- R / Pharma organizers
  + It is a fun and productive annual gathering. 
  + Please consider to share story and use cases to enlarge the community.

@@

- Training Material: https://r4csr.org/
- Demo project: 
  + Analysis project: https://github.com/elong0527/esubdemo
  + eCTD submission package: https://github.com/elong0527/ectddemo
- R Consortium FDA submission pilot: 
  + https://github.com/RConsortium/submissions-pilot1

- During the workshop, we will use `esubdemo` project.
  + `esubdemo` is shared in RStudio Cloud (https://rstudio.cloud/) 
  + Project link will be shared in chat
  + Post questions in group chat.
